Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
First draft of threats to validity.

>>>>

\subsection{Threats to validity}

The experimental evaluation in section~\ref{experimental-results} shows
a very positive evaluation of \tool over a diverse set of real-world
benchmarks. Nevertheless, the set of benchmarks is limited within the
scope of this paper and \tool's performance may not generalise to other
benchmark scenarios.

Furthermore, our algorithm to select suitable FWL word widths to model
plant behaviour employs a heuristic based on user-provided controller
word width specifications. Given the encouraging results of our benchmarks,
this heuristic appears to be strong enough for the current benchmark set,
but this may not hold in general. Further experiments towards determining
suitable plant FWL configurations may thus be necessary in future work.
